### 2020-05-25 writeup/transfer.tex
sec 3 wip

\section{Positive versus Negative Transfer in Multi-Task learning}
\label{sec_insight}

@@

\subsection{Model Shift Bias versus Variance Trade-off}\label{sec_main}

@@

\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}

@@

\textbf{Implications.} \todo{add connection to tasksonomy}

>>>>

\section{Revisiting the Bias-Variance Trade-off for Multi-Task learning}
\label{sec_insight}

@@

\subsection{Two Effects: Model Shift Bias and Variance Reduction}\label{sec_main}

@@

%\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}

@@
